---
title: "I am Noah Pollock"
date: "`r Sys.Date()`"
output: html_document
---

I'm excited about Data: extracting, processing, analyzing, reporting, dashboarding, and everything in between. For the past `r as.numeric(difftime(Sys.Date(),as.Date("2016-09-28"),unit="weeks"))/52.25` years, R has been my tool of choice. However, I have experience with a variety of sowftware, languages, and projects. You can read about my professional experience in my CV here. And just for fun, I recreated my CV below using ggplot!


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

You can also find me on LinkedIn: https://www.linkedin.com/in/noah-pollock-5b5804157/

```{r cv_dataframe}

cv_df <- data.frame(
  section = c(
    rep("Education",3)
    ,rep("Vocation",3)),
  text = c(
    "Bachelors of Arts in Psychology",
    "Masters of Science in Psychology",
    "Masters of Science in Information Technology Management",
    "Research Assistant/Data Transfer Specialist",
    "Research Area Intermediate",
    "Assistant Director of Assessment"),
  date = c("2013-04-01",
           "2015-04-01",
           "2020-04-01",
           "2012-04-01",
           "2016-01-28",
           "2016-09-28")
) %>%
  group_by(section) %>%
  mutate(y = 1:n())
```

## Including Plots

You can also embed plots, for example:

```{r cv_plot, echo=FALSE}

ggplot(cv_df,aes(x=1,y=y)) +
  geom_text(aes(label=text),hjust=0) +
  geom_text(aes(label=date,x=200),hjust=0) +
  facet_grid(section~.,switch = 'y') +
  scale_y_continuous(breaks = seq(1:nrow(cv_df))) +
  scale_x_continuous(limits = c(1,250))
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
