---
title: "I am Noah Pollock"
date: "`r Sys.Date()`"
output: html_document
---

I'm excited about Data: extracting, processing, analyzing, reporting, dashboarding, and everything in between. For the past `r round(as.numeric(difftime(Sys.Date(),as.Date("2016-09-28"),unit="weeks"))/52.25,2)` years, R has been my tool of choice. However, I have experience with a variety of sowftware, languages, and project types. You can learn more about me via the following resources:

* <a href="np_cv.pdf" target="_blank"> My Curriculum Vitae (aka my fancy resume) </a>
* <a href="https://www.linkedin.com/in/noah-pollock-5b5804157/" target="_blank"> LinkedIn </a>
* <a href="https://github.com/ncpollock/" target="_blank"> LinkedIn </a>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

Just for fun, I also recreated some of my CV using ggplot2.

First, I include some of my experiences in a dataframe. It would be more fun (and more efficient when it comes to updating) to scrape my actual CV, maybe I'll write about it as a blog post.

```{r cv_dataframe}

cv_df <- data.frame(
  section = c(
    rep("Education",3)
    ,rep("Vocation",3)
    ,rep("Acheivements",3)),
  text = c(
    "Bachelors of Arts in Psychology",
    "Masters of Science in Psychology",
    "Masters of Science in Information Technology Management",
    
    "Research Assistant/Data Transfer Specialist",
    "Research Area Intermediate",
    "Assistant Director of Assessment",
    
    "Chair, Michigan Association for Institutional Research",
    "Oakland University Advancement Core Value Award for Teamwork and Community",
    "John Steele Grant, Midwest Association of Colleges and Employers"),
  date = c("2013-04-01",
           "2015-04-01",
           "2020-04-01",
           
           "2012-04-01",
           "2016-01-28",
           "2016-09-28",
           
           "2020",
           "2018",
           "2018")
) %>%
  # arrange section the order it appears in dataframe
  mutate(section = factor(section, levels = unique(section))) %>% 
  group_by(section) %>%
  mutate(y = 1:n())

```

Now, I plot my cv!

```{r cv_plot, echo=FALSE}

ggplot(cv_df,aes(x=1,y=y)) +
  geom_text(aes(label=text),hjust=0) +
  geom_text(aes(label=date,x=250),hjust=1) +
  facet_grid(section~.,switch = 'y') +
  scale_y_continuous(breaks = seq(0,nrow(cv_df)+1,by=.5)
                     ,minor_breaks = seq(.25,nrow(cv_df)+1,by=1)
                     # ,minor_breaks = seq(0,nrow(cv_df)+1,by=.1)
                     ,limits = c(0.5,round((nrow(cv_df)+1)/length(unique(cv_df$section)),1)
                                 )) +
  scale_x_continuous(limits = c(1,250)) +
  ggtitle("Noah c. Pollock") +
  # expand_limits(x = 0.25, y = 0.25) +
  theme(panel.background = element_blank(),
        panel.border = element_rect(color='black',fill=NA),
      panel.grid.major.y = element_blank(),
      panel.grid.minor.y = element_line(color="gray"),
      # axis.line = element_line(colour="black"),
      axis.line = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank(),
      strip.background = element_rect(colour="#323232", fill='#323232'),
      strip.text = element_text(color="white"),
      plot.title = element_text(hjust = 0.5))
```

