---
title: "I am Noah Pollock"
date: "`r Sys.Date()`"
output: html_document
---

I'm excited about Data: extracting, processing, analyzing, reporting, dashboarding, and everything in between. For the past `r round(as.numeric(difftime(Sys.Date(),as.Date("2016-09-28"),unit="weeks"))/52.25,2)` years, R has been my tool of choice. However, I have experience with a variety of sowftware, languages, and projects. You can read about my professional experience in my CV below.

<a href="np_cv.pdf" target="_blank"> aka my fancy resume </a>

[My Curriculum Vitae (aka my fancy resume)](np_cv.pdf)



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

You can also find me on LinkedIn: https://www.linkedin.com/in/noah-pollock-5b5804157/

Just for fun, I also recreated some of my CV using ggplot2.

First, I include some of my experiences in a dataframe. It would be more fun (and more efficient when it comes to updating) to scrape my actual CV, maybe I'll write about it as a blog post.

```{r cv_dataframe}

cv_df <- data.frame(
  section = c(
    rep("Education",3)
    ,rep("Vocation",3)),
  text = c(
    "Bachelors of Arts in Psychology",
    "Masters of Science in Psychology",
    "Masters of Science in Information Technology Management",
    "Research Assistant/Data Transfer Specialist",
    "Research Area Intermediate",
    "Assistant Director of Assessment"),
  date = c("2013-04-01",
           "2015-04-01",
           "2020-04-01",
           "2012-04-01",
           "2016-01-28",
           "2016-09-28")
) %>%
  group_by(section) %>%
  mutate(y = 1:n())
```

Now, I plot my cv!

```{r cv_plot, echo=FALSE}

ggplot(cv_df,aes(x=1,y=y)) +
  geom_text(aes(label=text),hjust=0) +
  geom_text(aes(label=date,x=200),hjust=0) +
  facet_grid(section~.,switch = 'y') +
  scale_y_continuous(breaks = seq(1:nrow(cv_df))) +
  scale_x_continuous(limits = c(1,250)) +
  ggtitle("Noah c. Pollock") +
  theme(panel.background = element_blank(),
      panel.grid.major.y = element_blank(),
      panel.grid.minor.y = element_line(color="gray"),
      # axis.line = element_line(colour="black"),
      axis.line = element_blank(),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      axis.title = element_blank(),
      strip.background = element_rect(colour="#323232", fill='#323232'),
      strip.text = element_text(color="white"),
      plot.title = element_text(hjust = 0.5))
```

