---
title: "Blog"
author: "Noah Pollock"
date: "October 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(DT)
```

## Climbing Giants

This blog is my contribution to the fields of data science, business analytics, information technology, and variations on those themes.

[Test a link](index.html)

Some blog post ideas

* How I created this site: https://pages.github.com/
https://rmarkdown.rstudio.com/rmarkdown_websites.htm#publishing_websites

* Plot geometries on maps
* Tool to choose the cost effective pizza
* How to Kaggle: Huge disclaimer, this is my first competition
* Create your own test data that is actually interesting
* Encouraging steps toward graduation: Proof of concept
* ifelse trap with NA values


Read files in director for created and updated dates and times? Will that work in a server? Of course because rmarkdown are pre-rendered static html files!

## Blogs

```{r blog_df, echo=FALSE}
blog_df <- data.frame(
  filename = c("create_interesting_datasets"
               ,"pizza")
)

blog_df$created_at <- file.info(paste0(blog_df$filename,".html"))$ctime
blog_df$updated_at <- file.info(paste0(blog_df$filename,".html"))$mtime
blog_df$size <- file.info(paste0(blog_df$filename,".Rmd"))$size

#wrap filename in raw html
blog_df$filename <- paste0("<a href='",blog_df$filename,".html' target='_blank'>",blog_df$filename,"</a>")

# knitr::kable(blog_df)

# define formate for header
col_format <- JS(
  "function(settings, json) {",
  "$(this.api().table().header()).css({'background-color': '#252525', 'color': '#FFFFFF'});",
  "}")

datatable(blog_df
          ,escape = FALSE
          ,rownames=FALSE
          ,colnames = c('Blog Post Name',
                       'Created At',
                       'Updated At',
                       'Post Size (bytes)')
          ,options=list(
            initComplete = col_format,
            # searching=FALSE,
            # ordering=FALSE,
            pageLength=25,
            # bPaginate=FALSE,
            # bFilter=FALSE,
            columnDefs = list(list(className = 'dt-center',targets=2:ncol(blog_df)-1)), #center all but first column
            dom = 'frtpB'
          )) %>%
      formatStyle(
        'size',
        background = styleColorBar(range(0,max(blog_df$size)), 'gray'),
        backgroundSize = '98% 75%',
        backgroundRepeat = 'no-repeat',
        backgroundPosition = 'left')

# df <- data.frame(
#   variable = c("One Slice", "Leftover","dummy"),
#   value = c(12.5, 87.5,0)
# )
#
# bizarre pie charts!
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#   geom_col(width = 1) +
#   scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
#   coord_polar("y", start = pi / 3) +
#   geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
#   theme_void() + 
#   theme(legend.position = "none")
# 
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#   geom_col(width = 1) +
#   scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
#   coord_polar("y", start = pi / 3) +
#   geom_col(width = 1) +
#   coord_polar("y", start = 2) +
#   geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
#   geom_vline(xintercept = 1.5) +
#   theme_void() +
#   theme(legend.position = "none",
#         panel.background = element_blank())
# 
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#   geom_col(width = 1) +
#   scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
#   coord_polar("y", start = c(3,pi / 3)) +
#   geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
#   geom_vline(xintercept = 1.5) +
#   theme_void() + 
#   theme(legend.position = "none")
# 
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#   geom_col(width = 1) +
#   scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
#   coord_polar("y", start = c(3,9)) +
#   geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
#   # geom_vline(xintercept = 1.5) +
#   theme_void() + 
#   theme(legend.position = "none",
#         panel.background = element_blank())
# 
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#     geom_col(width = 1) +
#     scale_fill_manual(values = c('blue','blue', "blue")) + #"#d7b27c" "#752218"
#     coord_polar( start = c(6,7.5)) +
#     geom_point(aes(x=0,y=0),color="white",size=100,shape="☺") +
#     geom_vline(xintercept = 1.5) +
#     theme_void() + 
#     theme(legend.position = "none",
#           panel.background = element_blank())
```


