---
title: "Blog"
author: "Noah Pollock"
date: "October 18, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Climbing Giants

This blog is my contribution to the fields of data science, business analytics, information technology, and variations on those themes.


Some blog post ideas

* How I created this site: https://pages.github.com/
https://rmarkdown.rstudio.com/rmarkdown_websites.htm#publishing_websites

* Plot geometries on maps
* Tool to choose the cost effective pizza
* How to Kaggle: Huge disclaimer, this is my first competition
* Create your own test data that is actually interesting
* Encouraging steps toward graduation: Proof of concept

```{r pie, echo=FALSE}
library(ggplot2)
df <- data.frame(
  variable = c("One Slice", "Leftover","dummy"),
  value = c(12.5, 87.5,0)
)

ggplot(df, aes(x = "", y = value, fill = variable)) +
  geom_col(width = 1) +
  scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
  coord_polar("y", start = pi / 3) +
  geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
  theme_void() + 
  theme(legend.position = "none")

ggplot(df, aes(x = "", y = value, fill = variable)) +
  geom_col(width = 1) +
  scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
  coord_polar("y", start = pi / 3) +
  geom_col(width = 1) +
  coord_polar("y", start = 2) +
  geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
  geom_vline(xintercept = 1.5) +
  theme_void() +
  theme(legend.position = "none",
        panel.background = element_blank())

ggplot(df, aes(x = "", y = value, fill = variable)) +
  geom_col(width = 1) +
  scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
  coord_polar("y", start = c(3,pi / 3)) +
  geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
  geom_vline(xintercept = 1.5) +
  theme_void() + 
  theme(legend.position = "none")

ggplot(df, aes(x = "", y = value, fill = variable)) +
  geom_col(width = 1) +
  scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
  coord_polar("y", start = c(3,9)) +
  geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
  # geom_vline(xintercept = 1.5) +
  theme_void() + 
  theme(legend.position = "none",
        panel.background = element_blank())

ggplot(df, aes(x = "", y = value, fill = variable)) +
    geom_col(width = 1) +
    scale_fill_manual(values = c('blue','blue', "blue")) + #"#d7b27c" "#752218"
    coord_polar( start = c(6,7.5)) +
    geom_point(aes(x=0,y=0),color="white",size=100,shape="☺") +
    geom_vline(xintercept = 1.5) +
    theme_void() + 
    theme(legend.position = "none",
          panel.background = element_blank())
```


