---
title: '"Divide each difficulty into as many parts<br>as is feasible and necessary to resolve it."'
author: -Rene Descartes
output: 
  html_document:
    toc: no
    code_folding: hide
---

<style>
#header {
  background: url('images/main_banner_distort_blue.JPG') center no-repeat;
  background-size: cover;
  -webkit-background-size: cover;
  -moz-background-size: cover;
  -o-background-size: cover;
  color: white;
  text-align: center;
  height: 200px;
  position: relative;
  margin: 0 -30rem;
  padding: .25rem 0;
}
</style>
<br>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
library(DT)
library(dplyr)
```

This is my contribution to the fields of data science, business analytics, information technology, and related topics.

```{r blog_df}

# here I manually define which blog posts to include
blog_df <- data.frame(
  filename = c("create_interesting_datasets"
               ,"ifelse_NA_trap"
               ,"building_this_site"
               ,"ed_api"
               ,"monty_hall"
               ,"Report")
)
# eventually, I will read all .rmd files in main dir
  # and exclude non-blog posts because blog posts will 
    # quickly outnumber non-blog posts

# pull some text from each post for a content sample
blog_df$intros <- sapply(
  paste0(blog_df$filename,".Rmd"),function(x){
    paste0(substr(gsub(".*##",
     "",
     paste(readLines(x)[1:100],collapse = " "),
     perl = TRUE
    ),
    1,140)," ...")
    }
  )

# identify metadata
blog_df$created_at <- as.Date(file.info(paste0(blog_df$filename,".html"))$ctime)
blog_df$updated_at <- as.Date(file.info(paste0(blog_df$filename,".html"))$mtime)
blog_df$created_updated_at <- paste0(
  blog_df$created_at
  , " /<br>"
  , blog_df$updated_at
  )
blog_df$lines <- sapply(
  paste0(blog_df$filename,".Rmd"),function(x) blog_df$filename = length(readLines(x)))

# extract post titles
blog_df$titles <- sapply(
  paste0(blog_df$filename,".Rmd"),function(x){
    gsub('"',
         "",
         gsub("title: ",
           "",
           readLines(x)[2]
          )
    )
    }
  )

#wrap filename in raw html
#use post title as visible text
blog_df$filename <- paste0(
  "<h7> <a class='minimal' href='"
  , blog_df$filename
  , ".html' target='_blank'>"
  , blog_df$titles," "
  , "<i class='fa fa-sign-in fa-lg'></i>","</a></h7>")

# no longer need plain text titles
blog_df$titles <- NULL

blog_df <- blog_df %>%
  arrange(desc(created_at)) %>%
  select(-created_at,-updated_at)

# define formate for header
col_format <- JS(
  "function(settings, json) {",
  "$(this.api().table().header()).css({'background-color': '#252525', 'color': '#FFFFFF'});",
  "}")

datatable(blog_df
          ,escape = FALSE
          ,rownames=FALSE
          ,colnames = c('Title',
                        'Content Snippet',
                        'Created / Updated',
                       # 'Created At',
                       # 'Updated At',
                       'Post Length (lines)')
          ,options=list(
            autoWidth = TRUE,
            initComplete = col_format,
            pageLength=25,
            columnDefs = list( # center all but first column
              list(className = 'dt-center',targets=2)
              , list(className = 'dt-right',targets=3)
              , list(width = '100px', targets = c(2,3))
              , list(width = '250px', targets = 0)
              , list(verticalAlign = 'top', targets = "_all")), 
            dom = 'frtpB'
          )) %>%
        formatStyle(
        'lines',
        background = styleColorBar(range(0,max(blog_df$lines)), 'orange'),
        align = 'bottom',
        backgroundSize = '98% 45%',
        backgroundRepeat = 'no-repeat',
        backgroundPosition = 'left') %>%
      formatStyle(columns = "filename", 
              color = 'black',
              fontWeight = 'bold') %>%
      formatStyle(names(blog_df), 'vertical-align'='top')


```



