---
title: "Create Interesting Datasets"
author: "Noah Pollock"
date: "November 14, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: show

---

Let's create a dataset with *interesting* qualities. By interesting, I mean statistical effects such as mean differences between groups, variables that explain variability in other variables (and perhaps at variable levels!), and the ability to be charted and graphed in fun or useful ways.

For this post, we'll create these datasets purely with base R functions.

A few good reasons to create your own dataset:

* Mocking up visualizations
* Testing our understanding of statistics
* Simulations (e.g., probabilities or algorithms)
* Teaching

A few bad reasons:

* You didn't get enough responses to your survey
* Your effects are too small and p-values to large to publish

## Create the Dataset

```{r init_data}

set.seed(100) #specify number generator for 'random' numbers for reproducibility
n_students <- 1000 #number of grads
terms <- sort(rep(c(paste0(2014:2018,"10"),paste0(2013:2017,"40")),n_students))
n_terms <- length(unique(terms)) #number of terms generate
air_df <- data.frame(
  student_id = 1:(n_students*n_terms),
  term_code = terms,
  school = sample(c("BA","AS","EG"),size=n_students*n_terms,replace=TRUE),
  ATYP = rep(sample(c("F","T"),size=n_students,replace=TRUE),n_terms),
  sex = rep(sample(c("M","F"),prob=c(.55,.45),size=n_students,replace=TRUE),n_terms),
  residency = rep(sample(c("I","O"),size=n_students,replace=TRUE),n_terms),
  career_use = round(runif(n_students*n_terms,0,10)),
  post_grad_outcome = sample(c("Employed","Grad School","Still Seeking","Other"),prob=c(.64,.27,.07,.02),size=n_students*n_terms,replace=TRUE),
  
  # these vars are placeholders
  gpa = 0,
  salary = 0,
  stringsAsFactors = FALSE
)
air_df$gpa <- ifelse(air_df$ATYP=="F",
                     #intercept + slope*value + error/noise
                     #different slopes for a nice interaction effect
                     2.5 + .15*air_df$career_use + rnorm(n_students*n_terms,0,1),
                     3.7 + .01*air_df$career_use + rnorm(n_students*n_terms,0,1))
air_df$gpa = ifelse(air_df$gpa>4,runif(n_students*n_terms,3.2,4),air_df$gpa) # keep gpa under 4
air_df$gpa = ifelse(air_df$gpa<0,runif(n_students*n_terms,0,1),air_df$gpa) # keep gpa above 0

air_df$career_use <- ifelse(air_df$post_grad_outcome=="Employed",
                            #intercept + slope*value + error/noise
                            #different slopes for a nice interaction effect
                            sample(0:10
                                   ,prob=c(3:13)
                                   ,replace=TRUE
                                   ,size=length(
                                     air_df$career_use[air_df$post_grad_outcome=="Employed"])),
                            air_df$career_use)

air_df$salary <- ifelse(air_df$school=="EG",
                        #intercept + slope*value + error/noise
                        #different slopes for a nice interaction effect
                        64000 + 750*air_df$career_use + rnorm(n_students*n_terms,0,1000),
                        ifelse(air_df$school=="AS",
                               48000 + 10*air_df$career_use + rnorm(n_students*n_terms,0,4000),
                               51000 + 400*air_df$career_use + rnorm(n_students*n_terms,0,2700)))
air_df$salary <- ifelse(air_df$post_grad_outcome=="Employed",air_df$salary,NA)

```

## Show Interest

Let's discover how it's interesting.

```{r plots, echo=FALSE}
plot(pressure)

```

```{r stats, echo=FALSE}


```
