---
title: "NA Values in ifelse(): It's Not What You Think"
author: "Noah Pollock"
date: "December 4, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Scope
Do you know how ifelse() operates when faced with missing data? Are you sure you know? Read more to avoid catastrophic data errors when using ifelse().

## Introduction
Consider this plain english if then logic: 

**If** my Kaggle score is in the top 10%, **then** I am treating myself to a new laptop, **else** I'm taking away my Netflix privileges.

In short: Top 10% = New Laptop, Anything Else = No Netflix.

Obviously, if I don't enter a submission into Kaggle, my score cannot possibly be in the top 10%, therefore I should revoke my Netflix privileges! However, this is not how ifelse() evaluates this situation. Specifically, ifelse() only operates on non-missing values unless explicitly told to do otherwise.

## Example
Imagine I'm one of six people who all follow this same conditional logic, perform well in Kaggle and be rewarded, perform poorly or not at all and receive punishment [^1]. The others all at least put forth an effort and submitted. My `kaggle_score_percentile` is `NA` because I did not submit. I should have my Netflix revoked, and so should the others who did not score in the top 10%.

[^1]: Can you tell I studied Psychology?


```{r ifelse_fail}
# build a dataframe
test_df <- data.frame(
  kaggle_score_percentile = c(seq(5,29,5),NA)
)

knitr::kable(test_df,align = 'l') # see it

# apply conditional logic

ifelse(
  test_df$kaggle_score_percentile >=10, # conditional logic
  "New Laptop", # if true
  "No Netflix" # else (if false)
  ) 

```

Is that what you expected? `ifelse()` did not evaluate the way we might expect in natural langauge. My score did not meet the condition `kaggle_score_percentile >= 10`, but instead of receiving the else condition, I received an `NA`. In the same vein as `NA == NA` is not TRUE nor is it FALSE (it's `NA`) or for the MS Access users, you cannot join by missing values. 

Well, most of the time when I write conditional logic, I want the else condition to evaluate on missing values, so here's a workaround.

```{r ifelse_fix}
ifelse(
  test_df$kaggle_score_percentile >=10 # our logic from before
  & !is.na(test_df$kaggle_score_percentile), # explicit evaluation of na values
  "New Laptop",
  "No Netflix")
```
