---
title: "R Piece of the Pie"
author: "Noah Pollock"
date: "October 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pie_df <- data.frame(
  store = rep(c("Little Cesars","Jets","Hungry Howies","Papa Romanos","Giordanos"),3),
  size = rep(c("Small","Medium","Large"),5),
  price = 1:15
)
```

## Square Inches for Round Pizzas

Price per ounce, price per square foot, price per square inch.

I should allow user input to ocreate a tool that will determine the price per square inch and determine which of two pizzas you should purchase.

Would need digital calipers to determine thickness. But calories (e.g., high fat mozzarella vs low fat mozzarella).

```{r cars}


# df <- data.frame(
#   variable = c("One Slice", "Leftover","dummy"),
#   value = c(12.5, 87.5,0)
# )
#
# bizarre pie charts!
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#   geom_col(width = 1) +
#   scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
#   coord_polar("y", start = pi / 3) +
#   geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
#   theme_void() + 
#   theme(legend.position = "none")
# 
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#   geom_col(width = 1) +
#   scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
#   coord_polar("y", start = pi / 3) +
#   geom_col(width = 1) +
#   coord_polar("y", start = 2) +
#   geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
#   geom_vline(xintercept = 1.5) +
#   theme_void() +
#   theme(legend.position = "none",
#         panel.background = element_blank())
# 
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#   geom_col(width = 1) +
#   scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
#   coord_polar("y", start = c(3,pi / 3)) +
#   geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
#   geom_vline(xintercept = 1.5) +
#   theme_void() + 
#   theme(legend.position = "none")
# 
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#   geom_col(width = 1) +
#   scale_fill_manual(values = c(NA,NA, "#d7b27c")) + #"#d7b27c" "#752218"
#   coord_polar("y", start = c(3,9)) +
#   geom_point(aes(x=c(.8,1.2,1.3),y=c(7,10,5)),color="#752218",size=5) +
#   # geom_vline(xintercept = 1.5) +
#   theme_void() + 
#   theme(legend.position = "none",
#         panel.background = element_blank())
# 
# ggplot(df, aes(x = "", y = value, fill = variable)) +
#     geom_col(width = 1) +
#     scale_fill_manual(values = c('blue','blue', "blue")) + #"#d7b27c" "#752218"
#     coord_polar( start = c(6,7.5)) +
#     geom_point(aes(x=0,y=0),color="white",size=100,shape="☺") +
#     geom_vline(xintercept = 1.5) +
#     theme_void() + 
#     theme(legend.position = "none",
#           panel.background = element_blank())

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
