---
title: '"Ignorance more frequently begets confidence than does knowledge..."'
author: -Charles Darwin
output: 
  html_document:
    toc: no
    code_folding: none
---

<style>
#header {
  background: url('images/main_banner_distort_blue.JPG') center no-repeat;
  background-size: cover;
  -webkit-background-size: cover;
  -moz-background-size: cover;
  -o-background-size: cover;
  color: white;
  text-align: center;
  height: 200px;
  position: relative;
  margin: 0 -30rem;
  padding: .25rem 0;
}
</style>
<br>


These are a few of my personal projects. Each one is a work in progress, but some are more refined than others.

</div>
</div>
<div style="padding-right: 2%;">

```{r setup, include=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(shiny) #for html functions

# build clickable preview tiles
tile <- function(w = 4, s, t="Project Tile",a = "Clickable image redirecting to project site.",h=NA
                 , d = "This is the description."){
  column(w
         , a(href=h, target="_blank"
       , div(class=ifelse(!is.na(h),"img-tile","img-tile-inert")
             , p(strong(t),style="border-bottom: solid lightgray;")
             , div(style="text-align: center;"
                   , img( class="img-square"
                   , src=s
                   , alt=a)
             )
             , p(style="padding-top: 2%;"
                 , d))))
}
```


```{r test, results='asis'}
div(class="panel-body"
, fluidRow(
tile(s = "images/shiny_bi.JPG", t="Business Intelligence with Shiny",h="https://ncpolloc.shinyapps.io/shiny_bi/"
       , d = "Select or upload a dataset to explore and understand its variables and visualize relationships between variables.")
, tile(s = "images/data_generator.JPG", t="Fake Data Generator",h="https://ncpolloc.shinyapps.io/data_generator/"
       , d = "Need a dataset for testing or for class? This tool allows you to create and download a dataset.")
, tile(s = "images/rem.JPG", t="Random Employee Meetup",h="https://ncpolloc.shinyapps.io/REM_sample/"
       , d = "This web application connects employees for random meetups based upon their general availability.")
)
, fluidRow(
tile(s = "images/higher_ed.JPG", t="(Coming Soon!) Pure RMarkdown Dashboard on Higher Education"
       , d = "Gain insight into Higher Education and learn how RMarkdown can be leveraged to create dashboards without an R server.")
, tile(s = "images/bingo_landscape.JPG", t="Bingo Generator",h="https://ncpolloc.shinyapps.io/bingo/"
       , d = "Bingo, Bango, Bongo, whatever five letter word you call it and whatever theme you want it, you can create and download it.")
))
```



<br><br>
</div>
<div id="disqus_thread" class="container-fluid main-container"></div>
<script>

/**
*  RECOMMENDED CONFIGURATION VARIABLES: EDIT AND UNCOMMENT THE SECTION BELOW TO INSERT DYNAMIC VALUES FROM YOUR PLATFORM OR CMS.
*  LEARN WHY DEFINING THESE VARIABLES IS IMPORTANT: https://disqus.com/admin/universalcode/#configuration-variables*/

var disqus_config = function () {
this.page.url = 'https://ncpollock.github.io/projects.html';  // Replace PAGE_URL with your page's canonical URL variable
this.page.identifier = 'https://ncpollock.github.io/projects.html'; // Replace PAGE_IDENTIFIER with your page's unique identifier variable
};

(function() { // DON'T EDIT BELOW THIS LINE
var d = document, s = d.createElement('script');
s.src = 'https://nc-blog-1.disqus.com/embed.js';
s.setAttribute('data-timestamp', +new Date());
(d.head || d.body).appendChild(s);
})();
</script>
<noscript>Please enable JavaScript to view the <a href="https://disqus.com/?ref_noscript">comments powered by Disqus.</a></noscript>
