---
title: "Grab-Bag of Report Features"
author: 
- "Noah Pollock"
date: "January 2019"
output: 
  html_document:
    fig_width: 8.5
    df_print: kable
    code_folding: hide
    toc: FALSE
---

## Scope
See code and output for typical report features.

## Introduction
This is a report I produced as a teaching tool for the Pre-Conference Workshop at the Michigan Association for Institutional Research. I modified it slightly so it's for blog friendly (e.g., echo=TRUE on all code chunks), but the report was originally designed to be printed or saved as a PDF. Feel free to browse the report elements and expand the code chunmks that interest you. All the data here is fabricated. You can check-out [my post about creating interesting datasets](https://ncpollock.github.io/create_interesting_datasets.html) to learn more about how I created the data here and to see the full report in pdf form.

```{r include=TRUE,results='hide',message=FALSE,warning=FALSE}
#bootstrap themes: https://bootswatch.com/united/

knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
options(scipen=999) # avoid scientifit notation
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)
library(stringr)

# include geospatial plotting!
# learning resource and inspiration
# http://eriqande.github.io/rep-res-web/lectures/making-maps-with-R.html
library(maps)
library(gridExtra)
oi_colors <- c("gray","#EFE8E2","#323232","#a3a3a3","#88abfd","#4221ec")

roi_df <- data.frame(
  income_source = c("Minimum Wage",
                    "High School Diploma",
                    "Some College",
                    "10 Years after Attending OI",
                    "Bachelors"),
  amount = c(8.15*40*52, # source: Department of Labor Statistics
             26762, # source: https://factfinder.census.gov/faces/tableservices/jsf/pages/productview.xhtml?src=CF
             31801, # source: Census.gov ^
             43100, # source: college scorecard
             49711) # source: Census.gov ^
,stringsAsFactors = FALSE)

industry_df <- read.csv("datasets/industry_df.csv",
                        stringsAsFactors = FALSE)

air_df <- read.csv("datasets/air_df.csv",
                   stringsAsFactors = FALSE)

air_df <- air_df %>%
  rename(admit_type = ATYP) %>%
  mutate(
    school_recode = recode(school,
           "AS" = "Arts and Sciences",
           "BA" = "Business",
           "EG" = "Engineering and Computer Science"),
    year = substr(term_code,1,4),
    term_type = 
      ifelse(
        substr(term_code,5,6)=="10",
        "Winter",
        "Fall"),
    term_desc = 
      ifelse(
        substr(term_code,5,6)=="10",
        paste("Winter",substr(term_code,1,4),sep=" "),
        paste("Fall",substr(term_code,1,4),sep=" ")),
    career_use_bin = ifelse(career_use>0,"Engaged","Did Not Engage"), #use case_when instead?
    pg_outcome_bin = case_when(post_grad_outcome %in% 
                                 c("Employed","Grad School") ~ TRUE
                               ,post_grad_outcome %in% 
                                 c("Still Seeking","Other") ~ FALSE
                               )
    ) %>%
  left_join(industry_df,
            by="student_id") %>%
    select(-student_id)

```

## About the Data

Data was integrated from three sources: Banner, Handshake, and the First-Destination Survey results. While data from Banner and Handshake can be considered extremely accurate, the First-Destination Survey (FDS) results should be interpreted with the understanding that the information is self-reported by students within 6 months of graduation.


## Post-Graduation Outcomes
```{r post-grad-status,fig.align='center',fig.height=1.5}
air_df %>%
  group_by(post_grad_outcome) %>%
  rename(Outcome = post_grad_outcome) %>%
  summarise(Count=n()) %>%
  mutate(Percent=percent(Count/sum(Count)))

ggplot(air_df %>% 
         group_by(post_grad_outcome,school) %>%
         rename(Outcome = post_grad_outcome) %>%
         summarise(Count=n()) %>% 
         group_by(school) %>% 
         mutate(pct = Count/sum(Count))
       ,aes(x=school,y=pct,fill=Outcome)) +
  geom_col() +
  geom_text(aes(label=percent(pct,accuracy = 1),y=pct,group=Outcome),position = position_stack(.5)) +
  coord_flip() +
  scale_fill_manual(values=c(oi_colors[length(oi_colors)],oi_colors)) + 
  ggtitle("Figure 1: Post-Graduation Outcomes by School") + 
  theme(panel.background = element_blank(),
       panel.grid.major = element_blank(),
       axis.line.x   = element_blank(),
       axis.text.x = element_blank(),
       axis.line.y   = element_blank(),
       axis.title = element_blank(),
       axis.text.y = element_text(color='black'),
       legend.position="top",
       plot.title = element_text(hjust = 0.5))
```

```{r post-grad-status-time,fig.align='center',fig.height=3}

ggplot(
air_df %>%
         group_by(year) %>%
         count(pg_outcome_bin) %>%
  mutate(pct = n/sum(n)) %>%
  filter(pg_outcome_bin==TRUE,year!=2013)
,aes(x=year,y=pct,group=1)) +
  geom_area(aes(x=year,y=pct,group=post_grad_outcome,fill=post_grad_outcome),data=(air_df %>%
    group_by(year,post_grad_outcome) %>%
    count(pg_outcome_bin) %>% group_by(year) %>%
    mutate(pct = n/sum(n)) %>%
    filter(pg_outcome_bin==TRUE,year!=2013)),alpha=.7) +
  geom_line(size=1.5) +
  geom_point(size=3,color="black",fill = "white",stroke=2,shape=21) +
  scale_y_continuous(breaks = seq(0,1,.1),
                     labels = scales::percent(seq(0,1,.1))
                     ,limits = c(0,1)
                     ) +
  scale_fill_manual(values=c(oi_colors[length(oi_colors)],'black')) + 
  ggtitle("Figure 2: Post-Graduation Outcomes over Time") + 
  theme(panel.background = element_blank(),
       panel.grid.major.y = element_line(color = 'black'),
       panel.grid.minor.y = element_line(color = 'gray'),
       axis.line.x   = element_blank(),
       axis.text.x = element_text(color='black'),
       axis.line.y   = element_blank(),
       axis.title = element_blank(),
       axis.text.y = element_text(color='black'),
       legend.title = element_blank(),
       legend.position="top",
       plot.title = element_text(hjust = 0.5))

```


<P style="page-break-before: always">
## Post-Graduation Outcomes cont.

```{r mapping,fig.align="center"}

#note: I am creating dummy data on the fly for counts by region
states <- map_data("state")
states <- states %>%
  mutate(count = cut(1:nrow(states), #dummy data
                     c(-Inf,0, 1000, 5000, 10000, Inf),
                     labels=c("0","1-1k","1k-5k",'5k-10k','>10k')))

ggplot(data = states) + 
  geom_polygon(aes(x = long, y = lat, fill = count, group = group), color = "white") + 
  coord_fixed(1.3) +
  scale_fill_manual(values=c('gray80','gray50','black',oi_colors[length(oi_colors)])) +
  ggtitle("Employment by US State") +
  theme_void() +
  theme(legend.position = "left",
        plot.title = element_text(hjust = 0.5))


counties <- map_data("county")
counties <- subset(counties, region %in% c( "michigan"))

counties <- counties %>%
  mutate(count = cut(1:nrow(counties),
                     c(0, 100, 500, 1000, Inf),
                     labels=c("1-100","101-500",'501-1000','>1k')))

g1 <- ggplot(data = counties) + 
  geom_polygon(aes(x = long, y = lat, fill = count, group = group), color = "black") + 
  coord_fixed(1.3) +
  scale_fill_manual(values=c('gray80','gray50','black',oi_colors[length(oi_colors)])) +
  ggtitle("Employment by MI County") +
  theme_void() +
  theme(legend.position = "top",
        plot.title = element_text(hjust = 0.5,vjust = 3))


g2 <- ggplot(air_df %>%
         filter(!is.na(industry)) %>%
         count(industry) %>%
         arrange(n) %>%
         slice(1:10) %>%
         mutate(industry = factor(industry,levels=industry))
  ,aes(x=industry,y=n)) +
  geom_col() +
  coord_flip() +
  scale_x_discrete(labels = function(x) stringr::str_wrap(x,width=20)) +
  geom_text(aes(label=n),hjust=1.1 ) +
  scale_fill_manual(values=oi_colors) + 
  ggtitle("Top Industries Graduates Employed In") +
  theme(panel.background = element_blank(),
      legend.position = "none",
      axis.line.x   = element_blank(),
      axis.text.x = element_blank(),
      axis.line.y   = element_blank(),
      axis.title = element_blank(),
      axis.text.y = element_text(color='black'),
      axis.ticks = element_blank(),
      plot.title = element_text(hjust = 0.5))

grid.arrange(g1,g2,nrow=1)

```

<P style="page-break-before: always">
## Salary

Median annual salary for Our University graduates are observed to be higher than the yearly earnings of a full-time employee at minimum wage, a high school graduate with no college, an individual with some college, and graduates from other institutions.
```{r post-grad-salary}
knitr::kable(
air_df %>%
  filter(!is.na(salary)) %>%
  summarise(Count = n(),
            Median = median(salary)) %>%
  mutate(school="All") %>%
  bind_rows(air_df %>%
    filter(!is.na(salary)) %>%
    group_by(school) %>%
    summarise(Count = n(),
              Median = median(salary))) %>%
  select(school,everything()) %>%
  mutate(Median = scales::dollar(Median))
,caption="Table 2: Median annual salary by school.")

ggplot(roi_df %>% 
         bind_rows(air_df %>%
    summarise(income_source = "Our Institution Grads",
              amount = round(median(salary,na.rm=TRUE)))) %>%
      mutate(income_source = factor(income_source, levels = income_source))
  ,aes(x=income_source,y=amount,fill=income_source)) +
  geom_col() +
  coord_flip() +
    scale_x_discrete(labels = function(x) stringr::str_wrap(x,width=10)) +
  geom_text(aes(label=scales::dollar(amount)),hjust=1.1 ) +
  scale_fill_manual(values=oi_colors) + 
  ggtitle("Salary Estimates at Varying Education Levels") +
  theme(panel.background = element_blank(),
      legend.position = "none",
      axis.line.x   = element_blank(),
      axis.text.x = element_blank(),
      axis.line.y   = element_blank(),
      axis.title = element_blank(),
      axis.text.y = element_text(color='black'),
      axis.ticks = element_blank(),
      plot.title = element_text(hjust = 0.5))
```

<P style="page-break-before: always">
## Career Services Effectiveness

The charts and inferential statistics below show that engagement with Career Services is associated with post-graduation employment and salary. They also highlight differences by academic school. However, we cannot be sure that this association is causal. That is, other variables may account for the positive relationship between Career Services engagement and salary such as personality factors (e.g., students who are likely to seek out support services are also likely to acquire higher salaries).
```{r cu_x_school_to_sal}
cu_x_school_to_co_df <- air_df %>% 
  group_by(career_use_bin,school) %>%
  count(post_grad_outcome) %>%
  mutate(pct = n/sum(n)) %>%
  bind_rows(air_df %>% 
  group_by(career_use_bin) %>%
  count(post_grad_outcome) %>%
  mutate(pct = n/sum(n),
         school="All")) %>%
  filter(post_grad_outcome=="Employed")

ggplot(cu_x_school_to_co_df,
       aes(x=school,y=pct,fill=career_use_bin)) +
  geom_col(position="dodge") +
  geom_text(position = position_dodge(1), 
            vjust=-1.75,
            size = 2.5,
            aes(x = school,
                y = pct,
                group = career_use_bin,
                label=scales::percent(pct))) +
  labs(title = "Effect of Career Services Engagement on Employment",
       x="School",
       y="Employment Rate",
       fill = "Engaged with CS") + 
  scale_y_continuous(breaks=seq(0,1,0.1),limits = 0:1,
                     labels=scales::percent) +
  scale_fill_manual(values=c('black',oi_colors[length(oi_colors)])) + 
  theme(panel.background = element_blank(),
        legend.position = "top",
        panel.grid.major.y = element_line(color="gray"),
        panel.grid.minor.y=element_line(color="gray"),
        axis.line   = element_line(colour="black"),
        plot.title = element_text(hjust = 0.5))

cu_x_school_to_sal_df <- air_df %>% 
  group_by(career_use,school) %>% 
  summarise(gpa_mean = mean(gpa),
            salary_median = median(salary,na.rm = TRUE))

ggplot(cu_x_school_to_sal_df,
       aes(x=career_use,y=salary_median)) +
  facet_grid(~school) +
  geom_col(fill="#cdcdcd") +
  geom_line(size=2,colour=oi_colors[length(oi_colors)]) +
  geom_point(size=3,color="black",fill = oi_colors[length(oi_colors)],stroke=2,shape=21) +
  geom_text(position = position_dodge(width = .7),
            vjust=2.25,
            size = 2.5,
            aes(x = career_use,
                y = salary_median,
                # group = p_outcome,
                label=paste0(substr(salary_median,1,2),"k"))) +
  labs(title = "Effect of Career Services on FDS Salary",
       x="Engagements with Career Services",
       y="FDS Salary ($)",
       fill = NULL) + 
  scale_y_continuous(breaks=seq(0,max(cu_x_school_to_sal_df$salary_median),10000),
                     labels=format(
                       seq(0,max(cu_x_school_to_sal_df$salary_median),10000),big.mark = ","),
                     minor_breaks = seq(0, max(cu_x_school_to_sal_df$salary_median),5000)) +
  scale_x_continuous(breaks=0:max(cu_x_school_to_sal_df$career_use)) +
  theme(panel.background = element_blank(),
        panel.grid.major.y = element_line(color="gray"),
        panel.grid.minor.y=element_line(color="gray"),
        axis.line   = element_line(colour="black"),
        strip.background = element_rect(colour="#323232", fill='#323232'),
        strip.text = element_text(color="white"),
        plot.title = element_text(hjust = 0.5))

```

<P style="page-break-before: always">
## Supporting Inferential Statistics

#### Career Use Effect on Salary
```{r inf_stats,fig.align="left"}

stat_test <- summary(
lm(salary ~ career_use,
   data=air_df %>% filter(post_grad_outcome=="Employed"))
)

knitr::kable(data.frame(stat_test$r.squared),align="l")
knitr::kable(data.frame(stat_test$coefficients) %>%
               tibble::rownames_to_column("Variable") %>%
  mutate(Pr...t.. = format.pval(Pr...t..,eps=.001)) %>%
  rename("P Value" = Pr...t..))
```

#### Career Use and School Effect on Salary
```{r inf_stats2,fig.align="left"}
stat_test2 <- summary(
lm(salary ~ career_use + school,
   data=air_df %>% filter(post_grad_outcome=="Employed"))
)

knitr::kable(data.frame(stat_test2$r.squared),align="l")
knitr::kable(data.frame(stat_test2$coefficients) %>%
               tibble::rownames_to_column("Variable") %>%
  mutate(Pr...t.. = format.pval(Pr...t..,eps=.001)) %>%
  rename("P Value" = Pr...t..))
```

#### Interaction Effect of Career Use and School on Salary
```{r inf_stats3,fig.align="left"}

stat_test3 <- summary(
lm(salary ~ career_use * school,
   data=air_df %>% filter(post_grad_outcome=="Employed"))
)

knitr::kable(data.frame(stat_test3$r.squared),align="l")
knitr::kable(data.frame(stat_test3$coefficients) %>%
               tibble::rownames_to_column("Variable") %>%
  mutate(Pr...t.. = format.pval(Pr...t..,eps=.001)) %>%
  rename("P Value" = Pr...t..))

```
