---
title: '"Maybe stories are just data with a soul."'
author: -Brené Brown
output: 
  html_document:
    code_folding: none
    toc_float: false
---

<style>
#header {
  background: url('images/main_banner_distort_blue.JPG') center no-repeat;
  background-size: cover;
  -webkit-background-size: cover;
  -moz-background-size: cover;
  -o-background-size: cover;
  color: white;
  text-align: center;
  height: 200px;
  position: relative;
  margin: 0 -30rem;
  padding: .25rem 0;
}
</style>
<br>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE)
library(ggplot2)
library(DT)
```

##Public Datasets
A list of publicly available data.

```{r public_data, echo=FALSE}

# read in public dataset file
public_data_df <- read.csv("public_datasets.csv",
                    stringsAsFactors = FALSE)

#wrap filename in raw html
#give it the actual post title
public_data_df$Link <- paste0(
  "<a href='",public_data_df$Link,"' target='_blank'>",
  public_data_df$Name,"</a>")

# no longer need plain text titles
public_data_df$Name <- NULL

# define formate for header
col_format <- JS(
  "function(settings, json) {",
  "$(this.api().table().header()).css({'background-color': '#252525', 'color': '#FFFFFF'});",
  "}")

datatable(public_data_df
          ,escape = FALSE
          ,rownames=FALSE
          ,colnames = c('Dataset',
                        'Description')
          ,options=list(
            initComplete = col_format,
            pageLength=25,
            dom = 'frtpB'
          ))
```


##Learning Opportunities
A list of websites I found useful to learn more about R, data science, programming, and other fun stuff.

* [Professor Mark Isken's Website](http://www.sba.oakland.edu/faculty/isken/)
* [Dean Attali's Blog](https://deanattali.com/)


